Demand-aware geo-distributed placement for low latency

### 2015-07-05 auspice/bg.tex
added shrink, auspice, first draft background, intro edited
added abstract, small reference fixes in rest of thesis.

\newcommand{\indirection}{indirection-based routing}
\newcommand{\Indirection}{Indirection-based routing}
\newcommand{\Logcen}{Global name-to-address resolution}
\newcommand{\logcen}{global name-to-address resolution}
\newcommand{\namerouting}{name-based routing}
\newcommand{\Namerouting}{Name-based routing}

@@

%\blue{
(3) {\em Hierarchical names:} The hierarchical structure of DNS names is key to leveraging {\em federation} to scale to an arbitrary {number of names} by delegating different portions of the name space (or {zones}) to different organizations. For example, root name servers today only have to maintain state for a small number of top-level domain names.  In contrast, arbitrary or flat names, e.g., ``\verb+JohnSmith3142's watch+'' can not be supported in DNS while retaining the scaling benefits of federation as the root name servers would have to maintain nonzero state, e.g., at least the authoritative name server(s) and the DNSSEC key of a name, for essentially all names. Our position is that the design of a general-purpose global name service must not restrict the structure of names as names carry application-specific semantics; in $\S$\ref{sec:context}, we show examples of novel context-aware communication primitives that are feasible with unrestricted names.
%}

@@

% from 100 PlanetLab locations to authoritative name servers  for 318 domain names that are serviced by a leading managed DNS provider (refer to Section \ref{sec:managed}). 
%This finding suggests that managed DNS providers have considerable room for reducing lookup latencies with a more geo-distributed deployment of servers.

>>>>

@@

%\blue{
(3) {\em Hierarchical names:} The hierarchical structure of DNS names is key to leveraging {\em federation} to scale to an arbitrary {number of names} by delegating different portions of the name space (or {zones}) to different organizations. For example, root name servers today only have to maintain state for a small number of top-level domain names.  In contrast, arbitrary or flat names, e.g., ``\verb+JohnSmith3142's watch+'' can not be supported in DNS while retaining the scaling benefits of federation as the root name servers would have to maintain nonzero state, e.g., at least the authoritative name server(s) and the DNSSEC key of a name, for essentially all names. Our position is that the design of a general-purpose global name service must not restrict the structure of names as names carry application-specific semantics; in Section \ref{sec:context}, we show examples of novel context-aware communication primitives that are feasible with unrestricted names.
%}

@@

% from 100 PlanetLab locations to authoritative name servers  for 318 domain names that are serviced by a leading managed DNS provider (refer to Section \\ref{sec:managed}). 
%This finding suggests that managed DNS providers have considerable room for reducing lookup latencies with a more geo-distributed deployment of servers.

### 2015-07-05 auspice/design.tex
added abstract, small reference fixes in rest of thesis.

\begin{figure}[htbp]
	\vsp
	\begin{center}
		\includegraphics[width=3in,height=2in]{figure/DNS-GNS.pdf}
		\figvsp
		\caption{\small{DNS vs. GNS: Auspice can be deployed as a managed DNS provider today (left) or as a GNS provider that provides resolution service for its customer GUIDs (right). Name certification services bind a human-readable name to a GUID and its GNS provider, and certificate search services can help index and distribute certificates from all certification services. Solid (dotted) lines represent frequent (infrequent) query paths for a given mobile destination. Except for the tightly controlled DNS root  service, all services above are designed to be purveyed competitively.} 
		}\label{fig:DNS_GNS}
	\end{center}
	\figvsp
\end{figure}

@@

%Note that ``scalability'' is not an explicitly defined goal above because it is subsumed by the first three goals, i.e., a design maximizing performance and availability for any given resource cost is implicitly designed to improve the former with commensurately more resource expenditure. We explicitly quantify this tradeoff in $\S$\ref{sec:scalability}.

@@

{\bf{Extensibility.}} Our design cleanly separates the GNS provider's resource-intensive responsibility of name resolution under high mobility from the slow-changing certification process. It also allows for the GNS provider to be deployed today as a managed authoritative DNS provider (Fig. \ref{fig:DNS_GNS}) with the DNSSEC key deriving the GUID. Finally, the key-value store API enables an extensible name record representation. By default, each top-level key has associated read and write ACLs that could either be a blacklist or whitelist of GUIDs that respectively have read or write access. For example, a name record for GUID \verb+X+ that helps context-aware delivery or multihoming policies (detailed in $\S$\ref{sec:context}) is below.
\verb+{X:+
\verb+{IPs:[{IP: 23.55.66.43, plan: Unlimited}, {IP:+\\
\verb+62.44.65.75, plan: Limited}], geoloc: {[lat,long],+\\
\verb+readWhitelist:[Y,Z]}, multihome_policy:+
\verb+Unlimited}}+

@@

\begin{figure}[t]
	\centering
	\vspace{-0.3in}
	\includegraphics[scale=0.33]{gns-dns/gnrs.pdf}
	\vspace{-0.35in}
	\caption{Geo-distributed name servers in \auspice.  Replica-controllers  (logically separate from active replicas) decide placement of active replicas and active replicas handle requests from end-users. N1 is a globally popular name and is replicated globally; name N2 is  popular in select regions and is replicated in those regions.}
	\vspace{-0.2in}
	\label{fig:auspice}
\end{figure}

@@

%Unfortunately, the simplistic approach above has some problems. As the set of active replicas for a name can change over time, a write-to-one approach can lose the most recent write if the active replica that received the write crashes and before it recovers, the replica controllers change the set of active replicas. Even if the set of active replicas remains unchanged, the window of inconsistency (or unreachability) is higher with a write-to-one approach if the active replica that received the write fails. Most importantly, we anticipate that expressive name records (see $\S$\ref{sec:extsec}) may be updated by multiple authorized clients via different active replicas, and it is important to ensure that update operations (like appending to or deleting from a list) to a name are applied in the same order by all active replicas. These requirements motivate a state-machine approach to handle updates.

@@

\blue{
	{\bf{Comparison to DNS}.} All of the above analyses are applicable also to geo-replicated managed DNS providers were they to employ \auspice's demand-aware replication approach. The main difference between \auspice\ and today's managed DNS providers that rely on simplistic static replica placement schemes is in the lookup latency $l_i$ achieved for any given resource cost; we evaluate this performance-cost tradeoff extensively in our experiments ($\S$\ref{sec:comparison} and $\S$\ref{sec:managed}). 
}
\eat {
	As the group of active replicas can change over time, consistency guarantees depend on safely handling a change in the group of active replicas. The safety property can be stated as follows: {\em the group of active replicas in epoch $i+1$, before executing any requests, must obtain identical copies of the name record and that copy must include all committed updates to the name record made by the group of active replicas in epoch $i$}.

@@

%\textbf{Address lookups and updates:} Address update requests received by a replica are proposed to the Paxos instance between active replicas. When the update request is committed, a response is sent to the client. Lookup requests are processed locally at the replica. Sequential consistency for addresses lookups and updates is provided by sending the view along with responses to lookups/updates to the client as described in Section \ref{sec:consistency}.

@@

%The main justification for the above design is that it can achieve low enough connection outage times comparable to a home agent approach when nodes suddenly move mid-session, but without incurring the overhead of triangle routing or tunneling data traffic. We also note that the network-layer support for ``refresh resource record'' in $\S$\ref{sec:routing_client_requests} may also suffice as a notification to the sender, but the above proactive ``in-band'' scheme above is likely to be more responsive and can also be used when an endpoint wishes to migrate a connection for reasons other than mobility, e.g., from the cellular to WiFi interface. These arguments for using in-band communication for non-simultaneous mobility of endpoints are similar in spirit to several past proposals for session-level \cite{HIP,MPTCP} or connection-level \cite{ECCP,Serval,TCP-MIgrate,TCP-R} migration.

@@

\eat {
	\emph{(1) Eventual:} Paxos guarantees that all  replicas will eventually store identical copies of the name record. A lookup request can be simply processed locally at a replica as in $\S$\ref{sec:routing_client_requests}. %, which results in a lookup latency equal to the latency to the nearest replica and is sufficient to satisfy the eventual consistency requirement.

>>>>

\begin{figure}[htbp]
	\vsp
	\begin{center}
		\includegraphics[width=3in,height=2in]{figure/DNS-GNS.pdf}
		\caption{\small{DNS vs. GNS: Auspice can be deployed as a managed DNS provider today (left) or as a GNS provider that provides resolution service for its customer GUIDs (right). Name certification services bind a human-readable name to a GUID and its GNS provider, and certificate search services can help index and distribute certificates from all certification services. Solid (dotted) lines represent frequent (infrequent) query paths for a given mobile destination. Except for the tightly controlled DNS root  service, all services above are designed to be purveyed competitively.} 
		}\label{fig:DNS_GNS}
	\end{center}
	\figvsp
\end{figure}

@@

%Note that ``scalability'' is not an explicitly defined goal above because it is subsumed by the first three goals, i.e., a design maximizing performance and availability for any given resource cost is implicitly designed to improve the former with commensurately more resource expenditure. We explicitly quantify this tradeoff in Section \ref{sec:scalability}.

@@

{\bf{Extensibility.}} Our design cleanly separates the GNS provider's resource-intensive responsibility of name resolution under high mobility from the slow-changing certification process. It also allows for the GNS provider to be deployed today as a managed authoritative DNS provider (Fig. \ref{fig:DNS_GNS}) with the DNSSEC key deriving the GUID. Finally, the key-value store API enables an extensible name record representation. By default, each top-level key has associated read and write ACLs that could either be a blacklist or whitelist of GUIDs that respectively have read or write access. For example, a name record for GUID \verb+X+ that helps context-aware delivery or multihoming policies (detailed in Section \ref{sec:context}) is below.
\verb+{X:+
\verb+{IPs:[{IP: 23.55.66.43, plan: Unlimited}, {IP:+\\
\verb+62.44.65.75, plan: Limited}], geoloc: {[lat,long],+\\
\verb+readWhitelist:[Y,Z]}, multihome_policy:+
\verb+Unlimited}}+

@@

\begin{figure}[t]
	\centering
	\vspace{-0.3in}
	\includegraphics[scale=0.33]{gns-dns/gnrs.pdf}
	\vspace{-0.15in}
	\caption{Geo-distributed name servers in \auspice.  Replica-controllers  (logically separate from active replicas) decide placement of active replicas and active replicas handle requests from end-users. N1 is a globally popular name and is replicated globally; name N2 is  popular in select regions and is replicated in those regions.}
	\vspace{-0.2in}
	\label{fig:auspice}
\end{figure}

@@

%Unfortunately, the simplistic approach above has some problems. As the set of active replicas for a name can change over time, a write-to-one approach can lose the most recent write if the active replica that received the write crashes and before it recovers, the replica controllers change the set of active replicas. Even if the set of active replicas remains unchanged, the window of inconsistency (or unreachability) is higher with a write-to-one approach if the active replica that received the write fails. Most importantly, we anticipate that expressive name records (see Section \ref{sec:extsec}) may be updated by multiple authorized clients via different active replicas, and it is important to ensure that update operations (like appending to or deleting from a list) to a name are applied in the same order by all active replicas. These requirements motivate a state-machine approach to handle updates.

@@

\blue{
	{\bf{Comparison to DNS}.} All of the above analyses are applicable also to geo-replicated managed DNS providers were they to employ \auspice's demand-aware replication approach. The main difference between \auspice\ and today's managed DNS providers that rely on simplistic static replica placement schemes is in the lookup latency $l_i$ achieved for any given resource cost; we evaluate this performance-cost tradeoff extensively in our experiments (Section \ref{sec:comparison} and Section \ref{sec:managed}). 
}
\eat {
	As the group of active replicas can change over time, consistency guarantees depend on safely handling a change in the group of active replicas. The safety property can be stated as follows: {\em the group of active replicas in epoch $i+1$, before executing any requests, must obtain identical copies of the name record and that copy must include all committed updates to the name record made by the group of active replicas in epoch $i$}.

@@

%\textbf{Address lookups and updates:} Address update requests received by a replica are proposed to the Paxos instance between active replicas. When the update request is committed, a response is sent to the client. Lookup requests are processed locally at the replica. Sequential consistency for addresses lookups and updates is provided by sending the view along with responses to lookups/updates to the client as described in Section \\ref{sec:consistency}.

@@

%The main justification for the above design is that it can achieve low enough connection outage times comparable to a home agent approach when nodes suddenly move mid-session, but without incurring the overhead of triangle routing or tunneling data traffic. We also note that the network-layer support for ``refresh resource record'' in Section \ref{sec:routing_client_requests} may also suffice as a notification to the sender, but the above proactive ``in-band'' scheme above is likely to be more responsive and can also be used when an endpoint wishes to migrate a connection for reasons other than mobility, e.g., from the cellular to WiFi interface. These arguments for using in-band communication for non-simultaneous mobility of endpoints are similar in spirit to several past proposals for session-level \cite{HIP,MPTCP} or connection-level \cite{ECCP,Serval,TCP-MIgrate,TCP-R} migration.

@@

\eat {
	\emph{(1) Eventual:} Paxos guarantees that all  replicas will eventually store identical copies of the name record. A lookup request can be simply processed locally at a replica as in Section \ref{sec:routing_client_requests}. %, which results in a lookup latency equal to the latency to the nearest replica and is sufficient to satisfy the eventual consistency requirement.

### 2015-07-05 auspice/eval-case.tex
added abstract, small reference fixes in rest of thesis.

We evaluate the time-to-connect to a moving destination as a function of the mobility (or update) rate. The {\em end-to-end time-to-connect}  here is measured as the latency to look up an up-to-date address of the destination (or the time-to-connect as defined in $\S$\ref{sec:design_overview}) plus the time for msocket to successfully establish a TCP connection between the client and the mobile destination. This e2e-time-to-connect also incorporates the impact of timeouts and retried lookups if the client happens to have obtained a stale value (as in Fig. \ref{fig:4mobility}). The experiment is conducted on PlanetLab and consists of a single msocket client and a single mobile msocket server that is ``moving'' by changing its listening port number on a remote machine, and updating the name record replicated on three \auspice\ name servers accordingly. 
A successful connection setup delay using msocket is takes 2 RTTs (2 $\times$ 105 ms)  \cite{msocketTR}. 
As defined in Eq. \ref{eq:ttc}, the values of the update propagation latency $d_i$ and the lookup latency $l_i$ are 250 ms and 20 ms respectively, and the update rate $w_i$ varies from 1/1024/s to 1/s.
The timeout value ($T$) in our experiment is dependent on the RTT between the client and the server. If the client attempts to connect to the server on a port which the server is not listening on, the server immediately returns an error response to the client. Specifically, the timeout value is either 1 or 2 RTTs with equal probability depending on whether the connection failed during the first or the second round-trip of msocket's connection setup.
The client sends lookups at a rate of 10/s (but this rate does not affect the time-to-connect), and both lookups and updates inter-arrival times are exponentially distributed.

@@

%Context-aware group GUIDs in \auspice\ are active, i.e., \auspice\ refreshes the membership set periodically so that if an existing member leaves or a new member arrives into the context-space, the group GUID is updated accordingly. This refresh interval limits how responsive context-aware communication is to member churn. 
More details of optimizing context-aware queries in \auspice, reducing membership staleness, the connection migration protocol, etc. are outside the scope of this paper \cite{msocketTR}. This experiment seeks only to exemplify a powerful, new communication primitive enabled by context descriptors compared to strictly hierarchical DNS names, as argued in $\S$\ref{sec:whyNotDNS}.

>>>>

We evaluate the time-to-connect to a moving destination as a function of the mobility (or update) rate. The {\em end-to-end time-to-connect}  here is measured as the latency to look up an up-to-date address of the destination (or the time-to-connect as defined in Section \ref{sec:design_overview}) plus the time for msocket to successfully establish a TCP connection between the client and the mobile destination. This e2e-time-to-connect also incorporates the impact of timeouts and retried lookups if the client happens to have obtained a stale value (as in Fig. \ref{fig:4mobility}). The experiment is conducted on PlanetLab and consists of a single msocket client and a single mobile msocket server that is ``moving'' by changing its listening port number on a remote machine, and updating the name record replicated on three \auspice\ name servers accordingly. 
A successful connection setup delay using msocket is takes 2 RTTs (2 $\times$ 105 ms)  \cite{msocketTR}. 
As defined in Eq. \ref{eq:ttc}, the values of the update propagation latency $d_i$ and the lookup latency $l_i$ are 250 ms and 20 ms respectively, and the update rate $w_i$ varies from 1/1024/s to 1/s.
The timeout value ($T$) in our experiment is dependent on the RTT between the client and the server. If the client attempts to connect to the server on a port which the server is not listening on, the server immediately returns an error response to the client. Specifically, the timeout value is either 1 or 2 RTTs with equal probability depending on whether the connection failed during the first or the second round-trip of msocket's connection setup.
The client sends lookups at a rate of 10/s (but this rate does not affect the time-to-connect), and both lookups and updates inter-arrival times are exponentially distributed.

@@

%Context-aware group GUIDs in \auspice\ are active, i.e., \auspice\ refreshes the membership set periodically so that if an existing member leaves or a new member arrives into the context-space, the group GUID is updated accordingly. This refresh interval limits how responsive context-aware communication is to member churn. 
More details of optimizing context-aware queries in \auspice, reducing membership staleness, the connection migration protocol, etc. are outside the scope of this paper \cite{msocketTR}. This experiment seeks only to exemplify a powerful, new communication primitive enabled by context descriptors compared to strictly hierarchical DNS names, as argued in Section \ref{sec:whyNotDNS}.

### 2015-07-05 auspice/eval-part2.tex
added abstract, small reference fixes in rest of thesis.

%Managed DNS providers \cite{ultradns,dyndns,dnsmadeeasy} offer a geo-replicated DNS service, and are commonly purchased by enterprises today. This section compares \auspice\ to managed DNS providers in terms of lookup and update latencies.

@@

%To assess the sensitivity of \auspice's benefits to a broad range of system and workload parameters and scales, we develop a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior, and have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in $\S$\ref{sec:comparison}. We present one such experiment here, deferring others to a technical report \cite{techreport}.

@@

In order to assess the sensitivity of \auspice's performance and cost to a wider range of system parameters, workload parameters in $\S$\ref{sec:comparison}, and scales, we use a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior as in the PlanetLab experimental setup. We have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in the emulation in $\S$\ref{sec:comparison}.   Experiments here use 10K name servers, 2K local name servers, 10K service names, and 100K device names.

%We analyze the sensitivity of \auspice's benefits to the workload parameters used in $\S$\ref{sec:comparison}. In order to be able to explore a wider range of parameters and scales, we use a custom simulator that simulates round-trip latency, loss, and server load-vs-response time behavior as measured on PlanetLab. We have verified \cite{techreport} that the median latencies for all schemes in the simulator are within 8\% of that on PlanetLab for the experiment in $\S$\ref{sec:comparison}.   Experiments here use 10K nameservers, 2K local nameservers, 10K service names, and 100K device names.

@@

\blue{
\textbf{System parameters.} We also experiment with the system parameters in $\S$\ref{sec:design}, the fault tolerance threshold $F$, the capacity utilization $\mu$, and the randomness knob $\nu$. As expected, we find that as $F$ increases and approaches the total number of name servers, the cost and performance behavior increasingly mimics \static{F} until it is identical to \replicateall. Decreasing $\mu$ to small values makes \auspice's replication less aggressive hurting performance but reducing cost, while increasing $\mu$ much closer to 1 hurts latencies by overloading the system. The technical report \cite{techreport} describes these results as well as a slightly modified replica placement strategy that makes the random perturbation knob $\nu$ unnecessary (currently manually set to 0.5 in our experiments).
}
}

@@

%\textbf{Simulator validation:} We compare the results from our simulator to a PlanetLab experiment for  replication schemes in Section \ref{sec:schemes}. The median latencies for all schemes in the simulator are within 8\% of that on PlanetLab. The 95\%-ile latencies are higher on PlanetLab experiments than in the simulator due to unpredictable wide area latencies and server processing delays.

@@

\eat{
\textbf{Optimal:} We have compared \auspice\ to \optimal\ based on an optimization formulation of the placement problem \cite{techreport}. 
\optimal\ takes as input  the set of names, their request geo-distribution, the capacity of name servers, network latency between local name servers and name servers, and a load-vs-response-time curve at each name server, and computes replica placement so as to minimize the sum of  network and server latency.
%In Figure \ref{fig:optimal}, we present the ratio of latency of \auspice\ to \optimal\  from this experiment. 
For a similar workload as in Section \ref{sec:lookup},  we find that the latency for \auspice\ is between 1.1$\times$-2.1$\times$ of the \optimal\  across all load levels. \optimal\  performs better as it can globally optimize server resource allocation across all names, but \auspice\ uses a decentralized placement algorithm to independently decide replica placement for each name. 
In ongoing work, we are evaluating \optimal\  using the testbed; this is nontrivial partly because \optimal\ must know the exact load-vs-response time behavior, which is not always stationary or easy to measure, so we conjecture that the clean simulator environment overestimates the benefits of \optimal.
}

@@

% Can be removed
%\textbf{Analysis of \auspice\ design:} We study variants of \auspice's design and show that locality-awareness in the placement of replicas and redirecting to a replica based on both network and server load-induced latency are two major factors that reduces lookup latency for \auspice\ in the PlanetLab experiments  (Section \ref{sec:lowload}).

>>>>

%Managed DNS providers \cite{ultradns,dyndns,dnsmadeeasy} offer a geo-replicated DNS service, and are commonly purchased by enterprises today. This Section \compares \auspice\ to managed DNS providers in terms of lookup and update latencies.

@@

%To assess the sensitivity of \auspice's benefits to a broad range of system and workload parameters and scales, we develop a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior, and have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in Section \ref{sec:comparison}. We present one such experiment here, deferring others to a technical report \cite{techreport}.

@@

In order to assess the sensitivity of \auspice's performance and cost to a wider range of system parameters, workload parameters in Section \ref{sec:comparison}, and scales, we use a custom simulator that simulates round-trip delays, loss, and server load-vs-response time behavior as in the PlanetLab experimental setup. We have verified \cite{techreport} that the median latencies for all simulated schemes are within 8\% of those in the emulation in Section \ref{sec:comparison}.   Experiments here use 10K name servers, 2K local name servers, 10K service names, and 100K device names.

%We analyze the sensitivity of \auspice's benefits to the workload parameters used in Section \ref{sec:comparison}. In order to be able to explore a wider range of parameters and scales, we use a custom simulator that simulates round-trip latency, loss, and server load-vs-response time behavior as measured on PlanetLab. We have verified \cite{techreport} that the median latencies for all schemes in the simulator are within 8\% of that on PlanetLab for the experiment in Section \ref{sec:comparison}.   Experiments here use 10K nameservers, 2K local nameservers, 10K service names, and 100K device names.

@@

\blue{
\textbf{System parameters.} We also experiment with the system parameters in Section \ref{sec:design}, the fault tolerance threshold $F$, the capacity utilization $\mu$, and the randomness knob $\nu$. As expected, we find that as $F$ increases and approaches the total number of name servers, the cost and performance behavior increasingly mimics \static{F} until it is identical to \replicateall. Decreasing $\mu$ to small values makes \auspice's replication less aggressive hurting performance but reducing cost, while increasing $\mu$ much closer to 1 hurts latencies by overloading the system. The technical report \cite{techreport} describes these results as well as a slightly modified replica placement strategy that makes the random perturbation knob $\nu$ unnecessary (currently manually set to 0.5 in our experiments).
}
}

@@

%\textbf{Simulator validation:} We compare the results from our simulator to a PlanetLab experiment for  replication schemes in Section \\ref{sec:schemes}. The median latencies for all schemes in the simulator are within 8\% of that on PlanetLab. The 95\%-ile latencies are higher on PlanetLab experiments than in the simulator due to unpredictable wide area latencies and server processing delays.

@@

\eat{
\textbf{Optimal:} We have compared \auspice\ to \optimal\ based on an optimization formulation of the placement problem \cite{techreport}. 
\optimal\ takes as input  the set of names, their request geo-distribution, the capacity of name servers, network latency between local name servers and name servers, and a load-vs-response-time curve at each name server, and computes replica placement so as to minimize the sum of  network and server latency.
%In Figure \ref{fig:optimal}, we present the ratio of latency of \auspice\ to \optimal\  from this experiment. 
For a similar workload as in Section \\ref{sec:lookup},  we find that the latency for \auspice\ is between 1.1$\times$-2.1$\times$ of the \optimal\  across all load levels. \optimal\  performs better as it can globally optimize server resource allocation across all names, but \auspice\ uses a decentralized placement algorithm to independently decide replica placement for each name. 
In ongoing work, we are evaluating \optimal\  using the testbed; this is nontrivial partly because \optimal\ must know the exact load-vs-response time behavior, which is not always stationary or easy to measure, so we conjecture that the clean simulator environment overestimates the benefits of \optimal.
}

@@

% Can be removed
%\textbf{Analysis of \auspice\ design:} We study variants of \auspice's design and show that locality-awareness in the placement of replicas and redirecting to a replica based on both network and server load-induced latency are two major factors that reduces lookup latency for \auspice\ in the PlanetLab experiments  (Section \\ref{sec:lowload}).
